target_offtarget

### 2025-03-29 manuscript_figures.Rmd
update notebook

read_count <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab(" Log (Viral Reads)") +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  ylab("Log (Viral Reads)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_count_norm1 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts1),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(3, 1)) +
  ylab("Log (viral reads/cleaned reads)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

read_count_norm2 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = (Viral.load),
    y = log10(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(3, 1)) +
  ylab("Log (viral reads/cleaned reads/genome length)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(3, 1)) +
  ylab("Log (mean read depth)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

>>>>

read_count <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  ylab("Log (Viral Reads)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_count_norm1 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts1),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  ylab("Log (viral reads/cleaned reads)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

@@

read_count_norm2 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = (Viral.load),
    y = log10(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  ylab("Log (viral reads/cleaned reads/genome length)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))

read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid( ~ type, labeller = as_labeller(facet_names)) +
  theme_few() +
  theme(
    axis.title.x = element_text(size = 12),
    axis.text.x = element_text(angle = 0, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_linetype_manual(values=c(2, 1)) +
  ylab("Log (mean read depth)") +
  xlab("Genome copies") + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math()))
